---
title: "Student Performance"
author: Alina, Sasha, Katya, Sharvin
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Data
```{r echo = FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
library(dplyr)
student_data <- read.csv("~/Desktop/student_lifestyle_performance_dataset.csv")

head(student_data)
```
**This is our original data. We will clean it up a bit to only include useful parts for our analysis.**

```{r echo = FALSE, warning = FALSE, message = FALSE}
student_cleaned <- student_data %>%
  mutate(Attendance_Percentages = Attendance_Percentage /100)%>%
  select( Attendance_Percentages, Stress_Level_1_to_10) %>%
  rename(Stress_Rating = Stress_Level_1_to_10) %>%
  drop_na() %>%
  filter(Stress_Rating != 0.00) %>%
  arrange(Attendance_Percentages)
  

head(student_cleaned)


```


# Graph of Points
```{r echo = FALSE, warning = FALSE, message = FALSE}
ggplot(student_cleaned, aes(x = Attendance_Percentages, y = Stress_Rating)) +
  geom_point(color = "turquoise3") +
  geom_smooth(method = "lm", color = "darkorchid3")
```


# Residual Analysis
```{r echo = FALSE, warning = FALSE, message = FALSE}
stress_mod <- lm(Stress_Rating ~ Attendance_Percentages, data = student_cleaned)





stress_resids <- student_cleaned %>% 
  mutate(residuals = resid(stress_mod)) %>% 
  select(Attendance_Percentages, Stress_Rating, residuals)
  


stress_resids %>%
  ggplot(aes(x = Attendance_Percentages, y = residuals)) +
  geom_point(color = "turquoise3") +
  geom_hline(yintercept = 0, color = "darkorchid3")
```

## *Note
**When doing the residual analysis to check linear regression assumptions, we can see that out data has a megaphone shape, which means we don't have constant variance. We will keep this in mind as a shortcoming of our analysis of the data. **


# Hypothesis Testing


**Null hypothesis:** there is no relationship between class attendance and stress levels (slope = 0)

**Alternative hypothesis:** there is a positive relationship between class attendance and stress levels (slope > 0)

**Significance Level:** 0.05


# Result

Calculating test stat: 
```{r}
pt_est <- summary(stress_mod)$coefficients[2, 1]
se <- summary(stress_mod)$coefficients[2, 2]
n <- nrow(student_cleaned)

test_stat <- (pt_est - 0) / se

test_stat
```


Finding P-Value: 
```{r}
pt(test_stat, df = n-2, lower.tail = FALSE)
```

# Conclusion 

Since our p-value is less than 0.05, we have enough evidence to conclude that there **is** a positive relationship between class attendance and stress levels of students!
